%-------------------------
% Resume in Latex
% Author : Shubhi Rani
% License : MIT
%------------------------

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Mehran Attar}} \vspace{2mm}\\
  Ph.D. Candidate and Research Assistant,\\
  Location: Montreal, Quebec, Canada\\
  Email address: mehran.attar@concordia.ca \\
  Professional links: \href{https://www.linkedin.com/in/mehran-attar-1a241337/}{LinkedIn} $|$ \href{https://scholar.google.com/citations?user=nnLTy-oAAAAJ&hl=en}{GoogleScholar} $|$ \href{https://github.com/attarmehran}{GitHub}
\end{tabular*}
% \noindent\makebox[\linewidth]{\rule{19cm}{0.8pt}}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ph.D. in Information and Systems Engineering}{Sep. 2020 - Present}
      {Institute for Information Systems Engineering, Concordia University}{Montreal, Canada}
      
	   %{\scriptsize \textit{Research Topic: security of cyber-physical systems using machine learning algorithms}}
	    
    \resumeSubheading
      {M.Sc. in Electrical Engineering, Control Systems}{Sep. 2014 - March 2017}
      {School of Electrical and Computer Engineering, Tarbiat Modares University}{Tehran, Iran}
      
      \resumeSubheading
      {B.Sc. in Electrical Engineering, Control Systems}{Sep. 2009 - Feb. 2011}
      {School of Electrical Engineering, Sharif University of Technology}{Tehran, Iran}
      
      \resumeSubheading
      {B.Sc. in Electrical Engineering, Control Systems}{Jan. 2008 - July 2013}
      {School of Electrical Engineering, Hamedan University of Technology}{Hamedan, Iran}
      
  \resumeSubHeadingListEnd

%
%-----------Awards-----------------
\section{Honors and Awards}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Tuition Award of Excellence}{Sep. 2020}
      {Scholarship Prize}{Concordia University, Montreal, Canada}
      
      %%%
      
    \resumeSubheading
      {Ranked 3rd among all graduated students}{March 2017}
      {M.Sc. Graduated Student}{Tarbiat Modares University, Tehran, Iran}

%%%%

    \resumeSubheading
      {Semi-Finalist}{Dec. 2004}
      {National Chemistry Olympiad}{Tehran, Iran}
      
\resumeSubHeadingListEnd
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fields of Interest}
\begin{multicols}{3}
\begin{itemize}
    \item \textbf{Computer Science}\\
    Applied Machine Learning\\
    Reinforcement Learning\\
    Data Analysis\\
    Applied Deep Learning
    
    \item \textbf{Control Theory}\\
    Automatic Control\\
    Data-Driven Control\\
    Learning Control\\
    Convex Optimization
    
    \item \textbf{Industrial Applications}\\
    Wind Turbines\\
    Cyber-Physical Systems
\end{itemize}

\end{multicols}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Professional Experiences}
\subsection*{Industrial Experiences}

  \resumeSubHeadingListStart
    \resumeSubheading
      {Applied Machine Learning Engineer $\&$ Data Scientist}{April 2017 - Aug. 2021}
      {\href{https://mapnagroup.com/?lang=en}{MAPNA Group}}{Karaj, Iran}
      
	   {\small
	   \begin{itemize}
	       \item Anomaly detection in wind turbine using machine learning
methods based on SCADA data
%
\item Design and implementation of an online asset performance
monitoring system using intelligent algorithms for wind
turbines
	   \end{itemize}
	   
	   }
	   %%%%
	   \resumeSubheading
      {Control Systems Engineer}{April 2017 - Sep. 2018}
      {\href{https://mapnagroup.com/?lang=en}{MAPNA Group}}{Karaj, Iran}
      
	   {\small 
	   \begin{itemize}
	       \item Configuration of data acquisition systems, e.g., MC
Monitoring, VM-600, National Instrument System
%
\item Design and implementation of Kahak wind turbine simulator equipped with DFIG
	   \end{itemize}
	   
	   }
	   
  \resumeSubHeadingListEnd

\subsection*{Academic Experiences}
  %%%
    \resumeSubHeadingListStart
    \resumeSubheading
      {Research Scientist}{Sep. 2020 - Present}
      {\href{https://users.encs.concordia.ca/~wlucia/Group.html}{Cyber-Physical Systems Security Research Group}}{Montreal, Canada}
	   {\small
	   \begin{itemize}
	       \item Security of Cyber-Physical systems using machine learning methods
	       \item Develop intelligent algorithms for the security of naval vessels (Department of National Defence, Canada) \href{https://www.concordia.ca/news/stories/2022/11/21/the-department-of-national-defence-awards-concordia-researcher-1-m-to-develop-new-strategies-against-cyberattacks.html}{link}
	 \end{itemize}
	   }
	   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	   \resumeSubheading
      {Research Assistant}{Nov. 2015 - April 2017}
      {\href{https://www.modares.ac.ir/~majd}{Intelligent Control Systems Lab}}{Tarbiat Modares University, Tehran, Iran}
	   {\small
	   \begin{itemize}
	       \item Dynamical Modeling of Quadruped Robot Using Artificial Intelligence Models methods based on SCADA data
%
\item Design and Implementation a Controller for Quadruped Robot \href{https://www.researchgate.net/publication/315684334_Estimation_of_external_forces_acting_on_the_legs_of_a_quadruped_robot_using_two_nonlinear_disturbance_observers}{(TMUBOT)}
	   \end{itemize}}
	   
 \resumeSubHeadingListEnd
 
 
%--------PROGRAMMING SKILLS------------
\section{Software Skills}
\begin{multicols}{2}
\begin{itemize}
    \item \textbf{Programming Languages}: Python - MATLAB
    \item \textbf{Operating Systems}: Windows - Linux
    \item \textbf{Data Science Libraries}: Pandas - Numpy - Scipy
    \item \textbf{Plotting Libraries}: Matplotlib - Plotly
    \item \textbf{Documentation Tools}: LaTeX - MS Office
    \item \textbf{Version Control}: Git - GitHub
    \item \textbf{Machine Learning $\&$ Deep Learning Libraries}: Scikit-learn - Pytorch
\end{itemize}
\end{multicols}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%
\section{Journal publications}
\begin{enumerate}[label={[\arabic*]}]
  \item \textbf{Mehran Attar}, Walter Lucia, An Active Detection Strategy Based on Dimensionality Reduction for False
Data Injection Attacks in Cyber-Physical Systems," IEEE Transactions on Control of Network Systems, 2023. \href{https://ieeexplore.ieee.org/abstract/document/10042059}{link}
  \item \textbf{Mehran Attar}, Navid Dini, and Vahid Johari Majd, "Analysis and Design of a Time-Varying Linear
Extended State Observer for a Class of Nonlinear Systems with Unknown Dynamics Using Spectral
Lyapunov Function," Journal of Intelligent and Robotic Systems, vol. 94, pages 405-421, 2018. \href{https://link.springer.com/article/10.1007/s10846-018-0935-0}{link}
  \item \textbf{Mehran Attar}, Mohammadreza Dabirian, "Reinforcement Learning for Learning of Dynamical
Systems in Uncertain Environment: A Tutorial," arXiv preprint arXiv: 1905.07727, 2019. \href{https://arxiv.org/abs/1905.07727}{link}
\end{enumerate}

\section{Conference Proceedings}
\begin{enumerate}[label={[\arabic*]}]
  \item \textbf{Mehran Attar}, Mahdi Khodabandeh, "Design a Hybrid Model Predictive Controller for a DC-DC
Converter," 12th International Seminar on Power Electronics Technologies (TPES 2015), March 2015,
Sharif University of Technology, Tehran, Iran. (written in Persian)
  \item \textbf{Mehran Attar}, Navid Dini, Farid Edrisi and V.j.Majd, "Estimation of Decentralized Unknown Dynamics
for a 2DOF Manipulator Using a Time-Varying Extended State Observer" The 4th International
Conference on Robotics and Mechatronics (ICROM 2016), Oct 2016, University of Tehran, Tehran, Iran. \href{https://ieeexplore.ieee.org/document/7886827}{link}
  \item Farid Edrisi, Vahid Johari Majd, \textbf{Mehran Attar}, and Navid Dini, "Modifying the Attitude of Quadruped
Robot Body against Disturbances via Data," The 4th International Conference on Robotics and
Mechatronics (ICROM 2016), Oct 2016, University of Tehran, Tehran, Iran. \href{https://ieeexplore.ieee.org/document/7886817}{link}
%
\item Navid Dini, Vahid Johari Majd, Farid Edrisi and \textbf{Mehran Attar}, "Estimation of External Forces Acting on
the Legs of a Quadruped Robot using Two Nonlinear Disturbance Observers," The 4th International
Conference on Robotics and Mechatronics (ICROM 2016), Oct 2016, University of Tehran, Tehran, Iran. \href{https://ieeexplore.ieee.org/document/7886820}{link}
\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{References}

     \begin{itemize}
         \item \href{https://users.encs.concordia.ca/~wlucia/index.html}{\textbf{Prof. Walter Lucia}}\\ 
         Institute for Information Systems Engineering, Concordia University \\
         1455 de Maisonneuve Blvd. West, EV009.185 Montreal, Quebec, Canada, H3G 1M8\\
         Phone: (514) 848-2424 ext. 3982\\
         Email: \href{mailto: walter.lucia@concordia.ca}{ walter.lucia@concordia.ca}
         %
         \item \href{https://www.modares.ac.ir/~majd}{\textbf{Prof. Vahid Johari Majd}}\\
         Department of Electrical and Computer Engineering, Tarbiat Modares University\\
         P.O. Box 14115-194, Tehran, Iran\\
         Phone: (+9821) 82883353\\
         Email: \href{mailto: majd@modares.ac.ir}{ majd@modares.ac.ir}
     \end{itemize}
     
%-------------------------------------------
\end{document}